ABC inferences

### 2025-02-10 application_examples/abc_inferences/draft-abc-inferences-vignette.Rmd
Adding script get_CpG_positions.R

2. Get the CpG count in islands and non-island regions.

3. Filter CpG count to keep only regions with at least one CpG site and get the CpG position indeces for each region.

1. Save as simulation design the genomic structure for the regions within the selected genomic region, tree(s) -- GIVEN -- and sampled parameter combinations.

2. Run the simulations. TODO: Before submitting load package without devtools

>>>>

2. Get the CpG count in islands and non-island regions relative to the reference genome.

3. Filter the CpG count in islands and non-island regions for the genomic region of interest.

4. Get the spatial structure dataframe from the filtered GpG count to use as input for the simulations.

5. Save as simulation design the genomic structure for the regions within the selected genomic region, tree(s) -- GIVEN -- and sampled parameter combinations.

6. Run the simulations. TODO: Before submitting load package without devtools

7. Get the CpG position indices relative to the reference genome (cytosine index relative to positive strand).
